### 2017-07-25 lafaySimulatedScenePerception.tex
new annex figures

\begin{figure}[h]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_1}\label{fig:taxonomieEventa}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_2}\label{fig:taxonomieEventb}}\par
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_1}\label{fig:taxonomieTexturea}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_2}\label{fig:taxonomieTextureb}}
       \caption{Taxonomy of sound classes used for the simulation urban soundscapes: events (a,b) and textures (c,d).}
       \label{fig:taxonomie}
\end{figure}

>>>>

\begin{figure}[h]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_1_en}\label{fig:taxonomieEventa}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_2_en}\label{fig:taxonomieEventb}}\par
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_1_en}\label{fig:taxonomieTexturea}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_2_en}\label{fig:taxonomieTextureb}}
       \caption{Taxonomy of sound classes used for the simulation urban soundscapes: events (a,b) and textures (c,d).}
       \label{fig:taxonomie}
\end{figure}
